Refinements for open pNets

### 2021-07-09 2021-Refinement/paper/refinementarticle.tex
a bit of notations

\usepackage{amsmath}
%\usepackage{amsthm}
%\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{external}
\usepackage{hyperref}
\AtBeginDocument{\renewcommand\setminus{\smallsetminus}}

@@

>>>>

\usepackage{amsmath,amssymb}
%\usepackage{amsthm}
%\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{external}
\usepackage{hyperref}
\AtBeginDocument{\renewcommand\setminus{\smallsetminus}}

@@

\begin{definition}[Expression algebra, Action algebra, Formulas, Terms]
An expression algebra \(E\) is the disjoint union  of  terms,  actions, and  formulas
\( E=\terms \uplus \actions \uplus \formulas\) .
\(\terms\) and \(\actions\) are term algebras.
The formulas \(\formulas\) contain at least first order formulas and equality\footnote{Equality does not need to be only syntactic.} over \(\terms\) and \(\actions\).
\end{definition}

 \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder. An expression is closed if \(\fvars{e}=\emptyset\).
% The expressions restricted to variables in \(V\) are \(E_V := \mset{e \in E}{\fvars{e} \subseteq V}\).
%\defitem The closed expressions are expressions restricted to variables in \(\emptyset\), \(E_\emptyset\).

\TODO{on a besoin de quoi dans la suite?}

\begin{definition}[Values, Satisfiability, (Parallel) substitution]
We assume that the following are given:

$\bullet$ The values \(\values\), which are interpretations of closed terms.

$\bullet$ The satisfiability relation on closed formulas, \({\vdash} f\) where \(f \in \rformulas\).

$\bullet$ The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\).

$\bullet$ The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi: V \to \terms\), \(e\psubst{\psi}\).
\end{definition}
For the parallel substitution, the set \(V\) is not required to be a subset of \(\fvars{e}\).
In the case it isn't, the variables in \(V \setminus \fvars{e}\) are not substituted.
The substitutions might give a ill-formed expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
This can be guarded with the check \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitly be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.

The interpretation of terms is supposed to be decidable.
The satisfiability of formulas might not be decidable nor complete nor consistent,
but we will consider in the following that they are; this can be achieved by restricting the term algebra to a decidable subset.
For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, at least any property found satisfiable by the SMT is ensured to be true.
\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).

\subsection{Open Automata}\label{sec:def}
